First Season MWA EoR Power Spectrum Results at Redshift 7

### 2016-06-03 ms.tex
crossing ts and dotting lower case js

%\documentclass[preprint]{aastex}
%\documentclass[preprint2]{aastex}
%\documentclass{aastex}
\documentclass[iop]{emulateapj}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{natbib}
\usepackage{color}
\usepackage{hhline}
\usepackage{subfigure}
%\usepackage{bm,upgreek}
\usepackage{xspace}

@@

\DeclareAffil{ASU}{Arizona State University, School of Earth and Space Exploration, Tempe, AZ 85287, USA}
\DeclareAffil{UW}{University of Washington, Department of Physics, Seattle, WA 98195, USA}
\DeclareAffil{UWeSci}{University of Washington, eScience Institute, Seattle, WA 98195, USA}
\DeclareAffil{Brown}{Brown University, Department of Physics, Providence, RI 02912, USA}
\DeclareAffil{SKASA}{Square Kilometre Array South Africa (SKA SA), Park Road, Pinelands 7405, South Africa}
\DeclareAffil{RU}{Department of Physics and Electronics, Rhodes University, Grahamstown 6140, South Africa}
\DeclareAffil{CfA}{Harvard-Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA}
\DeclareAffil{ANU}{Australian National University, Research School of Astronomy and Astrophysics, Canberra, ACT 2611, Australia}
\DeclareAffil{CAASTRO}{ARC Centre of Excellence for All-sky Astrophysics (CAASTRO)}
\DeclareAffil{Haystack}{MIT Haystack Observatory, Westford, MA 01886, USA}
\DeclareAffil{MIT}{MIT Kavli Institute for Astrophysics and Space Research, Cambridge, MA 02139, USA}
\DeclareAffil{Curtin}{International Centre for Radio Astronomy Research, Curtin University, Perth, WA 6845, Australia}
\DeclareAffil{USydney}{The University of Sydney, Sydney Institute for Astronomy, School of Physics, NSW 2006, Australia}
\DeclareAffil{Dunlap}{Dunlap Institute for Astronomy and Astrophysics, University of Toronto, ON M5S 3H4, Canada}
\DeclareAffil{Victoria}{Victoria University of Wellington, School of Chemical \& Physical Sciences, Wellington 6140, New Zealand}
\DeclareAffil{UWisc}{University of Wisconsin--Milwaukee, Department of Physics, Milwaukee, WI 53201, USA}
\DeclareAffil{UMichigan}{University of Michigan, Department of Atmospheric, Oceanic and Space Sciences, Ann Arbor, MI 48109, USA}
\DeclareAffil{UMelbourne}{The University of Melbourne, School of Physics, Parkville, VIC 3010, Australia}
\DeclareAffil{CASS}{CSIRO Astronomy and Space Science (CASS), PO Box 76, Epping, NSW 1710, Australia}
\DeclareAffil{Tata}{National Centre for Radio Astrophysics, Tata Institute for Fundamental Research, Pune 411007, India}
\DeclareAffil{ASTRON}{Netherlands Institute for Radio Astronomy (ASTRON), PO Box 2, 7990 AA Dwingeloo, The Netherlands}
\DeclareAffil{RRI}{Raman Research Institute, Bangalore 560080, India}
\DeclareAffil{NRAO}{National Radio Astronomy Observatory, Charlottesville and Greenbank, USA}
\DeclareAffil{UWA}{International Centre for Radio Astronomy Research, University of Western Australia, Crawley, WA 6009, Australia}
\DeclareAffil{Berkeley}{Department of Astronomy, UC Berkeley, Berkeley, CA 94720, USA}
\DeclareAffil{RAL}{Radio Astronomy Laboratory, UC Berkeley, Berkeley, CA 94720, USA}
\DeclareAffil{BCCP}{Berkeley Center for Cosmological Physics, Berkeley, CA 94720, USA}

\affilauthorlist{
A.~P.~Beardsley\affils{ASU}\myemail,
B.~J.~Hazelton\affils{UW,UWeSci},
I.~S.~Sullivan\affils{UW},
P.~Carroll\affils{UW},
N.~Barry\affils{UW},
M.~Rahimi\affils{UMelbourne},
B.~Pindor\affils{UMelbourne,CAASTRO},
C.~M.~Trott\affils{Curtin,CAASTRO},
J.~Line\affils{UMelbourne,CAASTRO},
Daniel~C.~Jacobs\affils{ASU},
M.~F.~Morales\affils{UW}, 
J.~C.~Pober\affils{Brown,UW},
G.~Bernardi\affils{SKASA,RU,CfA},
Judd~D.~Bowman\affils{ASU},
M.~P.~Busch\affils{ASU},
F.~Briggs\affils{ANU,CAASTRO},
R.~J.~Cappallo\affils{Haystack}, 
B.~E.~Corey\affils{Haystack}, 
A.~de~Oliveira-Costa\affils{MIT},
Joshua~S.~Dillon\affils{Berkeley, RAL, BCCP,MIT},
D.~Emrich\affils{Curtin},
A.~Ewall-Wice\affils{MIT},
L.~Feng\affils{MIT},
B.~M.~Gaensler\affils{USydney,CAASTRO,Dunlap}, 
R.~Goeke\affils{MIT},
L.~J.~Greenhill\affils{CfA},
J.~N.~Hewitt\affils{MIT},
N.~Hurley-Walker\affils{Curtin},
M.~Johnston-Hollitt\affils{Victoria},
D.~L.~Kaplan\affils{UWisc}, 
J.~C.~Kasper\affils{UMichigan,CfA}, 
HS Kim\affils{UMelbourne,CAASTRO},
E.~Kratzenberg\affils{Haystack}, 
E.~Lenc\affils{USydney,CAASTRO},
A.~Loeb\affils{CfA},
C.~J.~Lonsdale\affils{Haystack}, 
M.~J.~Lynch\affils{Curtin}, 
B.~McKinley\affils{UMelbourne,CAASTRO},
S.~R.~McWhirter\affils{Haystack},
D.~A.~Mitchell\affils{CASS,CAASTRO}, 
E.~Morgan\affils{MIT}, 
A.~R.~Neben\affils{MIT},
N.~Thyagarajan\affils{ASU},
D.~Oberoi\affils{Tata}, 
A.~R.~Offringa\affils{ASTRON,CAASTRO}, 
S.~M.~Ord\affils{Curtin,CAASTRO},
S. Paul\affils{RRI},
T.~Prabu\affils{RRI}, 
P.~Procopio\affils{UMelbourne,CAASTRO},
J.~Riding\affils{UMelbourne,CAASTRO},
A.~E.~E.~Rogers\affils{Haystack}, 
A.~Roshi\affils{NRAO}, 
N.~Udaya~Shankar\affils{RRI}, 
Shiv~K.~Sethi\affils{RRI},
K.~S.~Srivani\affils{RRI}, 
R.~Subrahmanyan\affils{RRI,CAASTRO}, 
M.~Tegmark\affils{MIT},
S.~J.~Tingay\affils{Curtin,CAASTRO}, 
M.~Waterson\affils{Curtin,ANU},
R.~B.~Wayth\affils{Curtin,CAASTRO}, 
R.~L.~Webster\affils{UMelbourne,CAASTRO}, 
A.~R.~Whitney\affils{Haystack}, 
A.~Williams\affils{Curtin}, 
C.~L.~Williams\affils{MIT},
C.~Wu\affils{UWA},
J.~S.~B.~Wyithe\affils{UMelbourne,CAASTRO}
}

@@

\section{Analysis Pipeline}\label{sec:analysis}
In order to ensure consistency in analysis, the international MWA EoR collaboration has 
defined two independent reference analysis pipelines. The details of this strategy are 
outlined in \citealt{Jacobs:2016}. This study is based on the FHD-to-
\eppsilon pipe, which is in turn based on the Fast Holographic Deconvolution 
(FHD\footnote{\url{https://github.com/EoRImaging/FHD}}, \citealt{Sullivan:2012}) and Error 
Propagated Power Spectrum with Interleaved Observed Noise (\eppsilon
\footnote{\url{https://github.com/EoRImaging/eppsilon}}, B.~J.~Hazelton et al. 2016, in 
prep) packages. The general flow of the pipeline is shown in Figure~\ref{fig:pipe}, and we 
give an overview below. As a point of comparison, and to demonstrate robustness of the results, we compute the output power spectra with an independent calibration and power spectrum estimation pipeline, and demonstrate consistency.

@@

In the first calibration step we allow our complex gains to account for any direction-
independent response on a per antenna, per frequency channel, per polarization basis. To 
define our gains in this way, we have made two simplifications. First we push all direction-
dependence of the antenna response into the model of the primary beam. FHD is capable 
of using separate models for each antenna, though this has not yet been implemented for 
the MWA due to lack of individual models. The second simplification is to ignore any cross 
terms between our different axes, for example a mutual coupling between two antennas. In 
principle these terms would introduce baseline dependent gains, rather than antenna 
dependent. The MWA has not yet seen evidence of these terms, and so we currently 
neglect them in our solutions.

@@

In principle the foregrounds could be subtracted from the data immediately after calibration, 
before gridding and imaging. However, for diagnostic reasons, we have found it beneficial to 
carry the model through the entire pipeline, and only subtract just before squaring to power 
spectrum units, allowing to form power spectra of the dirty, model, and residual data.

@@

Moving up in the window, between the first two coarse band harmonic lines we can see an 
additional faint line. This is the re-emergence of the 150 meter cable reflections. While the 
method described in Section~\ref{subsec:cal_imaging} sufficiently calibrated out this 
reflection line for the three hour golden set integration, the lower noise level in this deeper 
integration shows it is not completely removed. Future analysis will require higher signal-to-
noise on the reflection fitting, which may require combining snapshots for calibration 
solutions.

@@

The RTS uses a fundamentally different calibration and foreground subtraction approach than 
FHD, as well as a different input point source model. The primary differences lie in the 
bandpass calibration, the use of ionospheric corrections, and the lack of a diffuse model. The 
calibration model uses a model with 1000 sources, for which ionospheric corrections are 
estimated and applied, before peeling of those sources from the dataset. The bandpass 
calibration is fundamentally different to FHD.
The bandpass for each antenna is fit to a 2nd order polynomial within each 1.28~MHz coarse 
band individually. The delay of the 150~m cable reflection discussed earlier is comparable
to the scale of the polynomial fit, so we expect it to naturally be fit out of the gain
solutions. Indeed the RTS has not yet seen evidence of the reflection in the processed
data \citep{Jacobs:2016}.
The CHIPS power 
spectrum estimator applies a full maximum-likelihood estimator to the data. In its full form, the 
data are weighted by the thermal noise, and a model for the residual point source signal, 
within a full frequency-dependent description of the instrument. For this comparison, the 
foreground weighting is not used, in order for a direct comparison with the weighting scheme 
used by \eppsilon.

@@

\section{Acknowledgements}
This work was supported by NSF grants AST-1410484 and AST-1206552.
JCP is supported by an NSF Astronomy and Astrophysics Fellowship under award 
AST-1302774. This scientific work makes use of the Murchison Radio-astronomy 
Observatory, operated by CSIRO. We acknowledge the Wajarri Yamatji people as the 
traditional owners of the Observatory site. Support for the MWA comes from the U.S. 
National Science Foundation (grants AST-0457585, PHY-0835713, CAREER-0847753, and 
AST-0908884), the Australian Research Council (LIEF grants LE0775621 and LE0882938), 
the U.S. Air Force Office of Scientific Research (grant FA9550-0510247), and the Centre for 
All-sky Astrophysics (an Australian Research Council Centre of Excellence funded by grant 
CE110001020). Support is also provided by the Smithsonian Astrophysical Observatory, the 
MIT School of Science, the Raman Research Institute, the Australian National University, 
and the Victoria University of Wellington (via grant MED-E1799 from the New Zealand 
Ministry of Economic Development and an IBM Shared University Research Grant). The 
Australian Federal government provides additional support via the Commonwealth Scientific 
and Industrial Research Organisation (CSIRO), National Collaborative Research 
Infrastructure Strategy, Education Investment Fund, and the Australia India Strategic 
Research Fund, and Astronomy Australia Limited, under contract to Curtin University. We 
acknowledge the iVEC Petabyte Data Store, the Initiative in Innovative Computing and the 
CUDA Center for Excellence sponsored by NVIDIA at Harvard University, and the 
International Centre for Radio Astronomy Research (ICRAR), a Joint Venture of Curtin 
University and The University of Western Australia, funded by the Western Australian State 
government.

>>>>

%\documentclass[preprint]{aastex}
%\documentclass[preprint2]{aastex}
%\documentclass{aastex}
\documentclass[iop]{emulateapj}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{natbib}
\usepackage{color}
\usepackage{hhline}
\usepackage{subfigure}
%\usepackage{bm,upgreek}
\usepackage{xspace}
\usepackage{hyperref}
\hypersetup{
     colorlinks   = true,
     allcolors    = blue
}

@@

\DeclareAffil{ASU}{Arizona State University, School of Earth and Space Exploration, Tempe, AZ 85287, USA}
\DeclareAffil{email}{e-mail: Adam.Beardsley@asu.edu}
\DeclareAffil{UW}{University of Washington, Department of Physics, Seattle, WA 98195, USA}
\DeclareAffil{UWeSci}{University of Washington, eScience Institute, Seattle, WA 98195, USA}
\DeclareAffil{Brown}{Brown University, Department of Physics, Providence, RI 02912, USA}
\DeclareAffil{SKASA}{Square Kilometre Array South Africa (SKA SA), Park Road, Pinelands 7405, South Africa}
\DeclareAffil{RU}{Department of Physics and Electronics, Rhodes University, Grahamstown 6140, South Africa}
\DeclareAffil{CfA}{Harvard-Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA}
\DeclareAffil{ANU}{Australian National University, Research School of Astronomy and Astrophysics, Canberra, ACT 2611, Australia}
\DeclareAffil{CAASTRO}{ARC Centre of Excellence for All-sky Astrophysics (CAASTRO)}
\DeclareAffil{Haystack}{MIT Haystack Observatory, Westford, MA 01886, USA}
\DeclareAffil{MIT}{MIT Kavli Institute for Astrophysics and Space Research, Cambridge, MA 02139, USA}
\DeclareAffil{Curtin}{International Centre for Radio Astronomy Research, Curtin University, Perth, WA 6845, Australia}
\DeclareAffil{USydney}{The University of Sydney, Sydney Institute for Astronomy, School of Physics, NSW 2006, Australia}
\DeclareAffil{Dunlap}{Dunlap Institute for Astronomy and Astrophysics, University of Toronto, ON M5S 3H4, Canada}
\DeclareAffil{Victoria}{Victoria University of Wellington, School of Chemical \& Physical Sciences, Wellington 6140, New Zealand}
\DeclareAffil{UWisc}{University of Wisconsin--Milwaukee, Department of Physics, Milwaukee, WI 53201, USA}
\DeclareAffil{UMichigan}{University of Michigan, Department of Atmospheric, Oceanic and Space Sciences, Ann Arbor, MI 48109, USA}
\DeclareAffil{UMelbourne}{The University of Melbourne, School of Physics, Parkville, VIC 3010, Australia}
\DeclareAffil{CASS}{CSIRO Astronomy and Space Science (CASS), PO Box 76, Epping, NSW 1710, Australia}
\DeclareAffil{Tata}{National Centre for Radio Astrophysics, Tata Institute for Fundamental Research, Pune 411007, India}
\DeclareAffil{ASTRON}{Netherlands Institute for Radio Astronomy (ASTRON), PO Box 2, 7990 AA Dwingeloo, The Netherlands}
\DeclareAffil{RRI}{Raman Research Institute, Bangalore 560080, India}
\DeclareAffil{NRAO}{National Radio Astronomy Observatory, Charlottesville and Greenbank, USA}
\DeclareAffil{UWA}{International Centre for Radio Astronomy Research, University of Western Australia, Crawley, WA 6009, Australia}
\DeclareAffil{Berkeley}{Department of Astronomy, UC Berkeley, Berkeley, CA 94720, USA}
\DeclareAffil{RAL}{Radio Astronomy Laboratory, UC Berkeley, Berkeley, CA 94720, USA}
\DeclareAffil{BCCP}{Berkeley Center for Cosmological Physics, Berkeley, CA 94720, USA}

\affilauthorlist{
A.~P.~Beardsley\affils{ASU,email},
B.~J.~Hazelton\affils{UW,UWeSci},
I.~S.~Sullivan\affils{UW},
P.~Carroll\affils{UW},
N.~Barry\affils{UW},
M.~Rahimi\affils{UMelbourne},
B.~Pindor\affils{UMelbourne,CAASTRO},
C.~M.~Trott\affils{Curtin,CAASTRO},
J.~Line\affils{UMelbourne,CAASTRO},
Daniel~C.~Jacobs\affils{ASU},
M.~F.~Morales\affils{UW}, 
J.~C.~Pober\affils{Brown,UW},
G.~Bernardi\affils{SKASA,RU,CfA},
Judd~D.~Bowman\affils{ASU},
M.~P.~Busch\affils{ASU},
F.~Briggs\affils{ANU,CAASTRO},
R.~J.~Cappallo\affils{Haystack}, 
B.~E.~Corey\affils{Haystack}, 
A.~de~Oliveira-Costa\affils{MIT},
Joshua~S.~Dillon\affils{Berkeley, RAL, BCCP,MIT},
D.~Emrich\affils{Curtin},
A.~Ewall-Wice\affils{MIT},
L.~Feng\affils{MIT},
B.~M.~Gaensler\affils{USydney,CAASTRO,Dunlap}, 
R.~Goeke\affils{MIT},
L.~J.~Greenhill\affils{CfA},
J.~N.~Hewitt\affils{MIT},
N.~Hurley-Walker\affils{Curtin},
M.~Johnston-Hollitt\affils{Victoria},
D.~L.~Kaplan\affils{UWisc}, 
J.~C.~Kasper\affils{UMichigan,CfA}, 
HS Kim\affils{UMelbourne,CAASTRO},
E.~Kratzenberg\affils{Haystack}, 
E.~Lenc\affils{USydney,CAASTRO},
A.~Loeb\affils{CfA},
C.~J.~Lonsdale\affils{Haystack}, 
M.~J.~Lynch\affils{Curtin}, 
B.~McKinley\affils{UMelbourne,CAASTRO},
S.~R.~McWhirter\affils{Haystack},
D.~A.~Mitchell\affils{CASS,CAASTRO}, 
E.~Morgan\affils{MIT}, 
A.~R.~Neben\affils{MIT},
N.~Thyagarajan\affils{ASU},
D.~Oberoi\affils{Tata}, 
A.~R.~Offringa\affils{ASTRON,CAASTRO}, 
S.~M.~Ord\affils{Curtin,CAASTRO},
S. Paul\affils{RRI},
T.~Prabu\affils{RRI}, 
P.~Procopio\affils{UMelbourne,CAASTRO},
J.~Riding\affils{UMelbourne,CAASTRO},
A.~E.~E.~Rogers\affils{Haystack}, 
A.~Roshi\affils{NRAO}, 
N.~Udaya~Shankar\affils{RRI}, 
Shiv~K.~Sethi\affils{RRI},
K.~S.~Srivani\affils{RRI}, 
R.~Subrahmanyan\affils{RRI,CAASTRO}, 
M.~Tegmark\affils{MIT},
S.~J.~Tingay\affils{Curtin,CAASTRO}, 
M.~Waterson\affils{Curtin,ANU},
R.~B.~Wayth\affils{Curtin,CAASTRO}, 
R.~L.~Webster\affils{UMelbourne,CAASTRO}, 
A.~R.~Whitney\affils{Haystack}, 
A.~Williams\affils{Curtin}, 
C.~L.~Williams\affils{MIT},
C.~Wu\affils{UWA},
J.~S.~B.~Wyithe\affils{UMelbourne,CAASTRO}
}

@@

\section{Analysis Pipeline}\label{sec:analysis}
In order to ensure consistency in analysis, the international MWA EoR collaboration has 
defined two independent reference analysis pipelines. The details of this strategy are 
outlined in \citealt{Jacobs:2016}. This study is based on the FHD-to-\eppsilon 
pipe, which is in turn based on the Fast Holographic Deconvolution 
(FHD\footnote{\url{https://github.com/EoRImaging/FHD}}, \citealt{Sullivan:2012}) and Error 
Propagated Power Spectrum with Interleaved Observed Noise (\eppsilon
\footnote{\url{https://github.com/EoRImaging/eppsilon}}, B.~J.~Hazelton et al. 2016, in 
prep) packages. The general flow of the pipeline is shown in Figure~\ref{fig:pipe}, and we 
give an overview below. As a point of comparison, and to demonstrate robustness of the results, we compute the output power spectra with an independent calibration and power spectrum estimation pipeline, and demonstrate consistency.

@@

In the first calibration step we allow our complex gains to account for any direction-independent 
response on a per antenna, per frequency channel, per polarization basis. To 
define our gains in this way, we have made two simplifications. First we push all 
direction-dependence of the antenna response into the model of the primary beam. FHD is capable 
of using separate models for each antenna, though this has not yet been implemented for 
the MWA due to lack of individual models. The second simplification is to ignore any cross 
terms between our different axes, for example a mutual coupling between two antennas. In 
principle these terms would introduce baseline dependent gains, rather than antenna 
dependent. The MWA has not yet seen evidence of these terms, and so we currently 
neglect them in our solutions.

@@

In principle the foregrounds could be subtracted from the data immediately after calibration, 
before gridding and imaging. However, for diagnostic reasons, we have found it beneficial to 
carry the model through the entire pipeline, and only subtract just before squaring to power 
spectrum units, allowing us to form power spectra of the dirty, model, and residual data.

@@

Moving up in the window, between the first two coarse band harmonic lines we can see an 
additional faint line. This is the re-emergence of the 150 meter cable reflections. While the 
method described in Section~\ref{subsec:cal_imaging} sufficiently calibrated out this 
reflection line for the three hour golden set integration, the lower noise level in this deeper 
integration shows it is not completely removed. Future analysis will require higher 
signal-to-noise on the reflection fitting, which may require combining snapshots for calibration 
solutions.

@@

The RTS uses a fundamentally different calibration and foreground subtraction approach than 
FHD, as well as a different input point source model. The primary differences lie in the 
bandpass calibration, the use of ionospheric corrections, and the lack of a diffuse model. The 
calibration model uses a model with 1000 sources, for which ionospheric corrections are 
estimated and applied, before peeling of those sources from the dataset. The bandpass 
calibration is fundamentally different to FHD.
The bandpass for each antenna is fitted to a 2nd order polynomial within each 1.28~MHz coarse 
band individually. The delay of the 150~m cable reflection discussed earlier is comparable
to the scale of the polynomial fit, so we expect it to naturally be fit out of the gain
solutions. Indeed the RTS has not yet seen evidence of the reflection in the processed
data \citep{Jacobs:2016}.
The CHIPS power 
spectrum estimator applies a full maximum-likelihood estimator to the data. In its full form, the 
data are weighted by the thermal noise, and a model for the residual point source signal, 
within a full frequency-dependent description of the instrument. For this comparison, the 
foreground weighting is not used, in order for a direct comparison with the weighting scheme 
used by \eppsilon.

@@

\section{Acknowledgements}
This work was supported by NSF grants AST-1410484 and AST-1206552.
DCJ is supported by an NSF Astronomy and Astrophysics Postdoctoral Fellowship
under award AST-1401708.
This scientific work makes use of the Murchison Radio-astronomy 
Observatory, operated by CSIRO. We acknowledge the Wajarri Yamatji people as the 
traditional owners of the Observatory site. Support for the MWA comes from the U.S. 
National Science Foundation (grants AST-0457585, PHY-0835713, CAREER-0847753, and 
AST-0908884), the Australian Research Council (LIEF grants LE0775621 and LE0882938), 
the U.S. Air Force Office of Scientific Research (grant FA9550-0510247), and the Centre for 
All-sky Astrophysics (an Australian Research Council Centre of Excellence funded by grant 
CE110001020). Support is also provided by the Smithsonian Astrophysical Observatory, the 
MIT School of Science, the Raman Research Institute, the Australian National University, 
and the Victoria University of Wellington (via grant MED-E1799 from the New Zealand 
Ministry of Economic Development and an IBM Shared University Research Grant). The 
Australian Federal government provides additional support via the Commonwealth Scientific 
and Industrial Research Organisation (CSIRO), National Collaborative Research 
Infrastructure Strategy, Education Investment Fund, and the Australia India Strategic 
Research Fund, and Astronomy Australia Limited, under contract to Curtin University. We 
acknowledge the iVEC Petabyte Data Store, the Initiative in Innovative Computing and the 
CUDA Center for Excellence sponsored by NVIDIA at Harvard University, and the 
International Centre for Radio Astronomy Research (ICRAR), a Joint Venture of Curtin 
University and The University of Western Australia, funded by the Western Australian State 
government.
